\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}

\hypersetup{
colorlinks=true,
citecolor=RedViolet,
linkcolor=RedViolet,
urlcolor=RedViolet
}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
\begin{list}{\ding{113}}{
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
		\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
\begin{list}{$\bullet$}{
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
		\setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{Page \thepage \hspace{1pt} of 2}

\begin{document}

\name{Mohammadreza Samadi \vspace{0.02in} \hspace{3.5in} \sl{\small Last Update: January 2021}}

\begin{resume}
	\section{\sc Contact Information}
	\begin{tabular}{@{}p{3.5in}p{4in}}
		Computer Engineering Dept.,& {\it Email:} \href{mailto:mhmd.samadi@aut.ac.ir}{mhmd.samadi@aut.ac.ir} \\            
		Amirkabir Univ. of Tech. (AUT), & {\it Gmail:} \href{mailto:mhmd.samadi76@gmail.com}{mhmd.samadi76@gmail.com} \\         
		424 Hafez Ave., Tehran, Iran & {\it Home-Page:}  \href{http://mhmdsmdi.github.io}{mhmdsmdi.github.io} \\       
		& {\it GitHub:} \href{http://github.com/mhmdsmdi}{github.com/mhmdsmdi}     \\ 
	\end{tabular}
	
	%----------------------------------------------------------------------------------------
	%	RESEARCH
	%----------------------------------------------------------------------------------------
	\section{\sc Research Interests}
	\hspace{0.03in}
	\begin{tabular}{@{}p{2in}p{2in}p{2in}}
		$\bullet$ Natural Language Processing & $\bullet$ Information Retrieval & $\bullet$ Data Mining \\            
		$\bullet$ Deep Learning &  $\bullet$ Machine Learning & $\bullet$ Artificial Intelligence \\         
	\end{tabular}
	
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Education}
	\begin{list2}
		\item {\href{https://ce.aut.ac.ir/en}{\textbf{Amirkabir University of Technology}}, (Tehran Polytechnic), Tehran, Iran} \\
		B.Sc., Computer Engineering, 2016 - 2020 (expected) \\
		GPA: \textbf{3.86}/4 $\simeq$ \textbf{18.06}/20\\
		$\diamond$ Bachelor’s Thesis: \textit{Implementation of a Persian Fake News Detection System and a Fake News Crawler Tool}
		\item \textbf{Mofid High School}, Tehran, Iran \\
		High School Diploma in Mathematics and Physics, 2012 - 2016 \\
		GPA: \textbf{19.67} / 20
	\end{list2}
	
	%----------------------------------------------------------------------------------------
	%	PUBLICATIONS
	%----------------------------------------------------------------------------------------
	\section{\sc Publications And \\ Preprints}
	\begin{list2}
		\item Kavehzadeh, P. \textbf{Samadi, M.} and Amir Haeri, M. \textit{``Unsupervised Anomaly Detection on Node Attributed Networks: A Deep Learning Approach.''}, \textbf{ICISS2021} (\textbf{accepted}).
		\item \textbf{Samadi, M.} and Momtazi, S. \textit{``Fake News Detection: Deep Semantic Representation with Enhanced Feature Engineering''}, \textbf{IP\&M} (submitted), January 2021.
		\item \textbf{Samadi, M.} and Momtazi, S. \textit{``Multi-Channel Convolutional Neural Networks for Detecting COVID-19 Fake News.''}, \textbf{Applied Soft Computing} (under review), December 2020.	
		\item \textbf{Samadi, M.} Mousavian, M. and Momtazi, S. \textit{``Deep Contextualized Text Representation and Learning for Fake News Detection.''}, \textbf{IP\&M} (under review), October 2020.
		\item \textbf{Samadi, M.} Mousavian, M. and Momtazi, S. \textit{``Persian Fake News Detection: a Deep Neural Representation and Deep Neural Learning Approach.''}, \textbf{TALLIP} (under review), September 2020.
		\item \textbf{Samadi, M.}, \textit{``Question Recommendation System Based on the Pair Similarity.''}, Technical Report, September 2019.
	\end{list2}
	
	%----------------------------------------------------------------------------------------
	%	RESEARCH SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Research And Work Experiences}
	\begin{list2}
		\item \textbf{Fake News Detection System}, \textit{Bachelor’s Thesis} \hfill \sl{\textit{April 2020 - present}} \\
		Study on implementing a Persian fake news detection system using state-of-the-art pre-trained models and novel deep neural classifiers. During this project, a Persian fake news crawler was developed for scraping fake news from Persian news agencies websites - \textit{Impl. in Python} \\
		$\diamond$ Under supervision of \href{mailto:momtazi@aut.ac.ir}{Prof. Momtazi}
		\vspace{0.05in}
		\item \textbf{Anomaly Detection in Attributed Graphs} \hfill \sl{September 2020 - December 2020} \\
		Research on detecting outlier nodes in graphs using variational autoencoders. In this study, nodes of the graph were represented by features vectors extracted with different graph embedding algorithm, and our proposed model can detect abnormal nodes in the graph - \textit{Impl. in Python} \\
		$\diamond$ Under supervision of \href{mailto:m.amirhaeri@utwente.nl}{Prof. Amir Haeri}
		\vspace{0.05in}
		\item \textbf{Question Recommendation System} \hfill \sl{\textit{May 2019 - November 2019}} \\
		Research Intern at \href{http://braineng.scs.ipm.ac.ir/}{IPM Brain Engineering Research Center} \\
		My first project in NLP during my undergraduate studies. The goal
		was to develop a recommendation system using common text similarity metrics
		and static word embedding methods for recommending medical questions in the
		realm of Ophthalmology - \textit{Impl. in Python} \\
		$\diamond$ Under supervision of \href{mailto:rezalashgari@ipm.ir}{Prof. Lashgari}
		\vspace{0.05in}
		
		\item \textbf{Android Developer}, SOP Company \hfill \sl{\textit{March 2018 - October 2019}} \\
		I was responsible for designing and developing a mHealth (mobile health) application and defining its software requirements.
		\vspace{0.05in}
		
		\item \textbf{Android Developer Intern}, Papillon Company \hfill \sl{\textit{June 2017 - August 2017}} 
	\end{list2}
	%----------------------------------------------------------------------------------------
	%	Technology SKILLS SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Technical \\ Skills} 
	\hspace{0.03in}
	\begin{tabular}{@{}p{8cm}p{8cm}}
		$\bullet$ \textbf{Programming \& Scripting Languages} &  $\bullet$ \textbf{Mobile Development} \\
		\hspace{0.07in} Python, Java, C, C\# & \hspace{0.07in} Android, React Native \\
		$\bullet$ \textbf{Machine Learning Tools} & $\bullet$ \textbf{Web Frameworks and Databases}\\
		\hspace{0.07in} TensorFlow, Keras, PyTorch, scikit-learn & \hspace{0.07in} Vue.js, Django, Flask, MySQL, SQLite
	\end{tabular}
	
	%----------------------------------------------------------------------------------------
	%	PROFESSIONAL EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Teaching Experiences}
	\begin{list2}
		\item{\textbf{Teaching Assistant, Applied Linear Algebra} \hfill \sl{\textit{Spring 2019}}} \\ 
		Under supervision of \href{mailto:mazlaghani@aut.ac.ir}{Prof. Amir Mazlaghani} 
		\vspace{0.05in}
		\item{\textbf{Teaching Assistant, Operating Systems} \hfill \sl{\textit{Spring 2019}}}\\ 
		Under supervision of \href{mailto:nastooh@aut.ac.ir}{Prof. Taheri Javan}
		\vspace{0.05in}
		\item{\textbf{Teaching Assistant, Computer Architecture} \hfill \sl{\textit{Spring 2019}}}\\ 
		Under supervision of \href{mailto:farbeh@aut.ac.ir}{Prof. Farbeh}
		\vspace{0.05in}
		\item{\textbf{Lecturer, Fundamentals of Android Development}, AUT \hfill \sl{\textit{March 2019}}} \\
		A 30-hour workshop was held at the Amirkabir University of Tech. for students to become familiar with Java programming and the fundamentals of developing Android applications.
	\end{list2} 
	
	%----------------------------------------------------------------------------------------
	%	ACADEMIC PROJECT SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Notable \\ Course \\ Projects}
	\begin{list2}
		\item \textbf{Information Retrieval} \\
		Developed a news search engine with the capability of crawling news, boolean and vector space searching, and enhanced by clustering and classification algorithms - \textit{Impl. in Python}
		\item \textbf{Data Mining} \\
		Famous Kaggle challenges were solved by different classifiers, regression models, and clustering algorithms - \textit{Impl. in Python}
		\item \textbf{Principles of Computational Intelligence} \\
		Implemented an RBF neural network which trained by ES (Evolutionary Strategy) algorithm - \textit{Impl. in Python}
		\item \textbf{Principles and Applications of Artificial Intelligence} \\
		Implemented an interactive video based on foreground and background subtraction using MOG2 and KNN algorithms - \textit{Impl. in Python}
		\item \textbf{Algorithm Design} \\
		Developed an algorithm for detecting community structures using label propagation with weighted coherent neighborhood propinquity - \textit{Impl. in Java}
	\end{list2}
	
	%----------------------------------------------------------------------------------------
	%	LANGUAGE
	%----------------------------------------------------------------------------------------
	\section{\sc Language \\ Skills} 
	\begin{list2}
		\item \textbf{English}: Fluent \\
		$\diamond$ \textbf{TOEFL iBT: 102/120} \hfill \sl{\textit{August 22, 2020}} \\
		\textit{Reading \textbf{28}/30, Listening \textbf{25}/30, Speaking \textbf{25}/30, Writing \textbf{24}/30} \\
		$\diamond$ \textbf{GRE General:} \hfill \sl{\textit{November 16, 2020}} \\
		\textit{Quantitative Reasoning: \textbf{166}/170, Verbal Reasoning: \textbf{142}/170 , Analytical Writing: \textbf{3}} \\
		\vspace{-0.3cm}
		\item \textbf{Persian}: Native
	\end{list2}
	%----------------------------------------------------------------------------------------
	%	ACHIEVEMENTS SECTION
	%---------------------------------------------------------------------------------------- 
	\section{\sc Honors And Awards}
	\begin{list2}
		\item \textbf{Ranked 333} in the Nationwide University Entrance Exam among all students
		in Mathematics and Physics (approximately 120,000), \textit{2016}
		\item Accepted in the first level of \textbf{Iranian Chemistry Olympiad Exam}, \textit{2014}
	\end{list2}
	
	
	%----------------------------------------------------------------------------------------
	%	REFERENCES SECTION
	%----------------------------------------------------------------------------------------
	\section{\sc Referencs} 
	\begin{list2}
		\item{\textbf{Saeedeh Momtazi}} \\
		Assistant Professor, CE Department, Amirkabir University of Technology \\
		Email: \href{mailto:momtazi@aut.ac.ir}{momtazi@aut.ac.ir}
		\item{\textbf{Maryam Amir Haeri}} \\
		Assistant Professor, OMD Department, University of Twente \\
		Email: \href{mailto:m.amirhaeri@utwente.nl}{m.amirhaeri@utwente.nl}
		\item{\textbf{Reza Lashgari}} \\
		Assistant Professor, Brain Eng. Research Center, Institute For Research In Fundamental Sciences\\
		Email: \href{mailto:rezalashgari@ipm.ir}{rezalashgari@ipm.ir}
	\end{list2} 
	
\end{resume}
\end{document}





